### 2024-07-17 conteudo/background/nlpsimilarity.tex
Fix grammar errors with grammarly free tier

\section{Text similarity detection methods}

The standard methodology for text similarity detection are based on building vector embeddings of
the texts and apply a distance function in these embeddings to measure the similarity between them. 
There are multiple methods for building vector embeddings, such as bag-of-words, TF-IDF, LSI, Word2Vec \citep{gensimlivro}. 
The recent works related to build vector embeddings uses Largue Language Models (LLM), for example the usage of BERT, ELMo 
and GPT \citep{llmsimilar}. The most popular distance function used by the literature are the cosine similarity 
defined by the formula \citep{cosineref}:

@@

Where $A$ and $B$ are the vector embeddings of the two texts. One of the advantages of the cosine similarity is that $SC(A,B)$ 
is a number between $0$ and $1$, where $SC(A,B)$ values more close to the number $1$ means that two vectors are more similar.

It is a famous fact that LLM have high computational cost, one example of such is a experiment done by Reimers and Gurevych for 
finding the most similar pair in a collection of 10,000 sentences, that required about 65 hours with BERT \citep{bertsimilar}. This 
is a similar magnitude of comparation pairs we want to do through our work and for this reason we chose to not use this kind of 
vector embedding method, but it is a valid solution for smaller codebases.

@@

Gensim is a open source python library \citep{gensim} which the owners declare themselves as "The fastest library 
for training of vector embeddings - Python or otherwise. The core algorithms in Gensim use battle-hardened, 
highly optimized and parallelized C routines." \citep{gensimsite}. For the velocity of gensim we chose to use this library
for doing our vector embeddings.

In this work we will not explore more alternatives for vector embeddings. We do not want to optimize the computational 
cost or the code clone detection to the state-of-art as they are not the main objectives of our research.

>>>>

\section{Text similarity detection methods}
\label{sec:similarity}.

The standard methodology for text similarity detection is grounded on building vector embeddings of 
the texts and applying a distance function in these embeddings to measure the similarity between them. 
There are multiple vector embedding methods proposed by the literature, such as bag-of-words, TF-IDF, 
LSI, and Word2Vec \citep{gensimlivro}.
Recent works related to building vector embeddings use Large Language Models (LLM), for example,
the work of Ethayarajh, which uses BERT, ELMo, and GPT \citep{llmsimilar}. 
The most popular distance function used by the literature is the cosine similarity defined by the formula
\citep{cosineref}:

@@

Where $A$ and $B$ are the vector embeddings of the two texts, an advantage of the cosine similarity is that $SC(A,B)$ is
a number between $0$ and $1$, where $SC(A,B)$ values closer to the number $1$ means that two vectors are more similar, 
it is usual to compare the cosine similarity to approximation to a probability value, transforming the values between 
$0$ and $1$ to a percentage between $0 \% $ and $100\%$, through our research, we will use the percentage form.

It is a famous fact that LLM has a high computational cost. An example of the high computational cost is an analysis 
done by Reimers and Gurevych to find the most similar pair in a collection of 10,000 sentences, 
which required about 65 hours with BERT \citep{bertsimilar}. 
We want to compare a similar magnitude of pairs in our work, so we decided not to use LLM for our vector embedding 
method, even though it is a valid solution for smaller codebases.

@@

Gensim is an open-source Python library \citep{gensim} which the owners declare themselves as "The fastest library 
for training of vector embeddings - Python or otherwise. The core algorithms in Gensim use battle-hardened, highly 
optimized and parallelized C routines." \citep{gensimsite}. For the velocity of Gensim, we chose to use this library 
for our vector embedding method.

In this work, we will not explore more alternatives for vector embeddings. We do not want to optimize the
computational cost or the code clone detection to the state of the art as they are not the main objectives 
of our research.

### 2024-07-17 conteudo/background/refactor.tex
Fix grammar errors with grammarly free tier

Fowler defines refactoring in his book as "a controlled technique for imporving the design of an existing code base. Its
essence is applying a series of small behavior-preserving transformations, each of which too small to be worth doing. However
the cumulative effect of each of these transformations is quite significant." \citep{refactorbook}. The elimination of detected 
code clone duplication is a refactoring task that necessitates the application of refactoring methods. 
Fowler presents multiples refactoring methods such as parameterize method, replace parameter with explicit methods and 
replace parameter with method \citep{refactorbook}. There is a briefly explanation of the methods used in our research below.

>>>>

Fowler defines refactoring in his book as "a controlled technique for improving the design of an existing code base. 
Its essence is applying a series of small behavior-preserving transformations, each of which is too small to be worth 
doing. However, the cumulative effect of each of these transformations is quite significant." \citep{refactorbook}. 
The elimination of detected code clone duplication is a refactoring task that necessitates the 
application of refactoring methods. Fowler presents multiple refactoring methods such as the 
\textit{parameterize method}, the \textit{replace parameter with explicit methods} and 
the \textit{replace parameter with method} \citep{refactorbook}. 
There is a brief explanation of the methods used in our research below.
